Estimation of Fractional-N PLL Linearity Limits and Cycle Slipping

### 2025-06-12 CaseStudies/Example3_3_IntegerNSynthesizerDesignedforSettlingTime/article/article.qmd

f_o = fo_1 = 2.4e9
omega_o_1 = 2 * np.pi * fo_1

fo_2 = 2.4835e9
omega_o_2 = np.pi * 2 * fo_2

@@

zeta=0.707
```

@@

f_range = fo_2 - fo_1
tuning_range_percent = 9.6 
tuning_range = fo_1 / tuning_range_percent
Vdd=2
KVCO = Kvco = 250e6 # Hz/V
KVCO_ang = Kvco_ang = Kvco*2*math.pi
```

@@

f_c=(fo_1 + fo_2) / 2
fvco = f_min = f_c - tuning_range
f_max=f_c+tuning_range
```

@@

C_1 = C1 = 5e-9
A0 = 1

I_CP_ang = C_1 * 2 * math.pi * N1 * omega_n**2 / Kvco_ang / A0
I = I_CP = C_1 * 2 * math.pi * N1 * omega_n**2 / Kvco / A0
K_theta = Kphase = I_CP / (2 * np.pi)

@@

R_1 = R1 = 2 * zeta * omega_n / K
C_2 = C2 = C_1 / 10 
```

>>>>

fo_1_ex = 2.4e9
fo_2_ex = 2.4835e9
fo_1__fo_2 = fo_1_ex/fo_2_ex

f_o = fo_1 = 300e6
omega_o_1 = 2 * np.pi * fo_1

fo_2 = fo_1 * fo_1__fo_2
omega_o_2 = np.pi * 2 * fo_2

@@

zeta = 0.707
```

@@

f_range = fo_2 - fo_1
tuning_range_percent = 9.6 
tuning_range = fo_1 / tuning_range_percent
Vdd = 2
KVCO = Kvco = fo_1/tuning_range_percent # Hz/V
KVCO_ang = Kvco_ang = Kvco*2*math.pi
```

@@

f_c=(fo_1 + fo_2) / 2
f_min = f_c - tuning_range
f_max=f_c+tuning_range
#fvco = f_min
fvco = f_o
```

@@

C_1 = C1 = 5e-9
A0 = 6.258

I_CP_ang = C_1 * 2 * math.pi * N1 * omega_n**2 / Kvco_ang / A0
I = I_CP = C_1 * 2 * math.pi * N1 * omega_n**2 / Kvco / A0

K_theta = Kphase = I_CP / (2 * np.pi)

@@

R_1 = R1 = 2 * zeta * math.sqrt(1 / (K * C1))
C_2 = C2 = C_1 / 10 
```

### 2025-06-12 CaseStudies/Example3_4_SimulationandEstimationofLoopSettlingTimes/article/article.qmd

fvco = f_o = 4e9 # Hz
omega_o = 2 * np.pi * f_o # rad/s
N = 100
Kvco = KVCO = 200e6 # Hz/V
Kvco_ang = 2 * np.pi * Kvco # rad/s/V
I_CP = I = 100e-6
K_theta = Kphase = I / (2 * np.pi) # A/rad
A0 = 6.258
K = A0 * Kphase * KVCO / N
```

@@

| **Symbol**       | **Description**        | **Value**                                       |
|------------------|------------------------|-------------------------------------------------|
| $C_1$            | Series capacitor       | `{python} format(C_1)`F                         |
| $R_1$            | Series resistor        | `{python} format(R_1)`$\Omega$                  |
| $C_2$            | Shunt capacitor        | `{python} format(C_2)`F                         |
| $f_\mathrm{VCO}$ | VCO freq.              | `{python} format(fvco)`Hz                       |
| $K_\mathrm{VCO}$ | VCO sensivity          | `{python} format(Kvco)`Hz/V                     |
| $\theta_{e_m}$   | Max. Phase Error       | `{python} format_with_pi_latex(theta_e_m)`rad   |
| $I_\mathrm{CP}$  | CP Current             | `{python} format(I_CP)`A                        |
| $A_0$            | DC Gain                | `{python} format(A0)`                           |
| $f_\mathrm{bw}$  | Bandwidth              | `{python} format(f_bw)`Hz                       |
| $f_r$            | Ref. freq.             | `{python} format(f_r)`Hz                        |
| $N$              | Divider                | `{python} format(N)`                           |
| $\Delta f_m$     | Max. Step freq.        | `{python} format(step_m_lin)`Hz                 |
| $t_s$            | Settling time          | `{python} format(t_s)`s                         |
| $T_s$            | 3 MHz Acquisition time | `{python} format(T_s)`s                         |

>>>>

fvco = f_o = 4e9 # Hz
omega_o = 2 * np.pi * f_o # rad/s
N = 100
Kvco = KVCO = 2 * np.pi * 200e6 # rad/s/V
Kvco_lin = Kvco / (2 * np.pi) # Hz/V
I_CP = I = 100e-6
K_theta = Kphase = I / (2 * np.pi) # A/rad
A0 = 1
K = A0 * Kphase * KVCO / N
```

@@

| **Symbol**       | **Description**        | **Value**                                       |
|------------------|------------------------|-------------------------------------------------|
| $C_1$            | Series capacitor       | `{python} format(C_1)`F                         |
| $R_1$            | Series resistor        | `{python} format(R_1)`$\Omega$                  |
| $C_2$            | Shunt capacitor        | `{python} format(C_2)`F                         |
| $f_\mathrm{VCO}$ | VCO freq.              | `{python} format(fvco)`Hz                       |
| $K_\mathrm{VCO}$ | VCO sensivity          | `{python} format(Kvco_lin)`Hz/V                 |
| $\theta_{e_m}$   | Max. Phase Error       | `{python} format_with_pi_latex(theta_e_m)`rad   |
| $I_\mathrm{CP}$  | CP Current             | `{python} format(I_CP)`A                        |
| $A_0$            | DC Gain                | `{python} format(A0)`                           |
| $f_\mathrm{bw}$  | Bandwidth              | `{python} format(f_bw)`Hz                       |
| $f_r$            | Ref. freq.             | `{python} format(f_r)`Hz                        |
| $N$              | Divider                | `{python} format(N)`                            |
| $\Delta f_m$     | Max. Step freq.        | `{python} format(step_m_lin)`Hz                 |
| $t_s$            | Settling time          | `{python} format(t_s)`s                         |
| $T_s$            | 3 MHz Acquisition time | `{python} format(T_s)`s                         |
